### 2018-06-04 README.Rmd
update site and add logo
add lifecycle badge
update README with updated badge, fixes #80

# visdat

@@

[![Travis Build Status](https://travis-ci.org/ropensci/visdat.svg?branch=master)](https://travis-ci.org/ropensci/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ropensci/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/ropensci/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/ropensci/visdat/master.svg)](https://codecov.io/github/ropensci/visdat?branch=master)

@@

>>>>

# visdat <img src="man/figures/visdat-logo.png" align="right" />

@@

[![Travis Build Status](https://travis-ci.org/ropensci/visdat.svg?branch=master)](https://travis-ci.org/ropensci/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/ropensci/visdat/master.svg)](https://codecov.io/github/ropensci/visdat?branch=master)

@@

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
